Identifying regime transitions for water governance: Take the Yellow River Basin in China as case

### 2023-05-12 paper/main/02_methods.tex
docs(paper): :memo: 更新SFV的方法叙述，符号说明提前

	Where $SFV_i$ is the scarcity-flexibility-variability (SFV) index of region $i$. By taking water flexibility and variability into account, the SFV focus more on dynamic responses to water resources in a developing perspective, which is a valid metric of temporal changes in water stresses~\cite{qin2019}. To apply this method, we need to combine three metrics following:

@@

	In all the equations above, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.

@@

	where $p_{i}$ is the water proportion of region $i$ to the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).

>>>>

	Where $SFV_i$ is the scarcity-flexibility-variability (SFV) index of region $i$. By taking water flexibility and variability into account, the SFV focus more on dynamic responses to water resources in a developing perspective, which is a valid metric of temporal changes in water stresses~\cite{qin2019}. To apply this method, we need to combine three metrics: scarcity, flexibility and variability.
	In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.

@@

@@

	where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
docs(paper): :memo: 更新Pettitt方法应用的数据描述
docs(paper): :memo: 更新SFV的方法叙述，符号说明提前

\subsection{Comment \#3}
% 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
\RC{} Equations: what is the CEM in equation (7)? Also, what does the water proportion refer to? Some of the terms in equation (2) in Supporting Information are not explained. e.g. R or WU.

@@

>>>>

\subsection{Comment \#3}
% 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
\RC{} Equations: what is the CEM in equation (7)? Also, what does the water proportion refer to? Some of the terms in equation (2) in Supporting Information are not explained.\ e.g. R or WU.\

\AR{} Thanks for the comment. ``CEM'' should be ``AEM'' -the indicator we applied for IA.\ This has been revised in the new manuscript:

\begin{quote}
    \begin{equation}
		I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
	\end{equation}
\end{quote}

\AR*{} Also, sorry about the misunderstanding term. We modified the sentence with ``water proportion'' to:

\begin{quote}
    where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
\end{quote}

% 很抱歉关于SFV计算的部分也造成了困惑。实际上我们提到了这些符号的意义，只不过是在所有公式之后。这的确会造成误解，因此在返修后的文章中我们将这段叙述放到了公式之前：
\AR*{} Sorry that the part about SFV calculation also caused confusion. We actually mentioned the meaning of these symbols, but only after all the equations since they shared the same symbols. This indeed can be misleading, so in the revised article we put this statement before the formula:

\begin{quote}
    In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
\end{quote}

@@

\AR{} Thanks for pointing it out! Pettitt approach was applied to IWGI time series data. We now clarify that in the method section:

\begin{quote}
    We applied the Pettitt (1979) approach to detect change-points of IWGI within continuous data, since this method has no assumptions about the distribution of the data~\cite{pettitt1979}.
\end{quote}
